### 2013-02-16 doc/icml2013/regression.tex
edit

Finally, $\eta_3(x)$ contains five terms plus an additional bias since the estimator uses $\hat M_1$ rather than $M_1$.
There are two additional considerations.
First, to bound $\hat\E_3[\epsilon^3]$, we use Lemma 19 of \cite{hsu13spherical}.
Second, the additional bias is small by the previous bound (and it is constructed on $\sD_1$, which is independent of $\sD_3$
used to construct $\hat M_3$.
Therefore, we incur another $O(\sigma^2 \cdot R \sigma \sqrt{\frac{\log(1/\delta_1)}{n}})$.
Handling the other terms using conventional means
$\|\hat\E_3[\eta_3(x) x\tp{3}]\|_\op = O(R^3 (L^3 R^3 + \sigma L^2 R^2 + \sigma^2 L R + \sigma^3 + \sigma^3 R) \sqrt{\frac{\log^3(1/\delta_1)}{n}})$.
Finally, taking $\delta_1 = \delta/3$, and taking the union bound,
we get our result, where we are bounding quantities fairly crudely for the sake of simplicity.
\end{proof}

>>>>

Finally, $\eta_3(x)$ contains five terms plus an additional bias since the estimator uses $\hat M_1$ rather than $M_1$.
There are two additional considerations.
First, to bound $\hat\E_3[\epsilon^3]$, we use Lemma 19 of \cite{hsu13spherical}.
Second, the additional bias is small by the previous bound (and it is constructed on $\sD_1$, which is independent of $\sD_3$
used to construct $\hat M_3$.
Therefore, we incur another $O(\sigma^2 \cdot R \sigma \sqrt{\frac{\log(1/\delta_1)}{n}})$.
We can handle the other terms using conventional means.
Combining everything, we obtain
$\|\hat\E_3[\eta_3(x) x\tp{3}]\|_\op = O(R^3 (L^3 R^3 + \sigma L^2 R^2 + \sigma^2 L R + \sigma^3 + \sigma^3 R) \sqrt{\frac{\log^3(1/\delta_1)}{n}})$.

Finally, taking $\delta_1 = \delta/3$, and taking the union bound over the bounds for $p \in \{1,2,3\}$,
we get our result.
Note that we are bounding quantities fairly crudely for the sake of simplicity.
\end{proof}
